Evolutionary algorithms in a volunteer computing system: performance assessment

### 2016-03-11 PPSN2016/paper.Rnw
Rewrite abstract
I have done several changes, mainly on the client, as well as extensive experiments. Main change now is that overlap is almost entirely eliminated, that is, it is quite improbable that the clients started in a previous experiment contribute to a new one. However, this also makes changes in behavior of the users: they see changes if they leave it long enough. So let's see what goes on.

So far only thing changed is title and abstract. Please @mariosky @unintendedbear @fergunet take a look

@@

@@

these.experiments <- c("nooverlap-0","nooverlap","nooverlap-newgraph","nooverlap-newgraph-reboot-cachecrash")

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-per-minute-cache=32-",i,".csv"))
    time.data <- rbind(time.data,
                       data.frame(Experiment=rep(i,length(this.data$IPs)),
                                  minute=strptime(this.data$time,"%Y-%m-%d %H:%M"),
                                  IPs=as.integer(this.data$IPs))
                       )
}
@

\title{The human in the loop: volunteer computing as a socio-technical
system}

@@

\begin{abstract}
Volunteer computing is a form of distributed computing where users
decide on their participation and the amount of time and other
resources they will ``lend''. This makes them an essential part of the
algorithm and of the performance of the whole system. As a
sociotechnical system, this participation follows some patterns and in
this paper we examine the result of several volunteer distributed
evolutionary computation experiments and try to find out which are
those patterns and what makes an experiment successful or not,
including the feedback loop that is created between the users and the
algorithm itself. In this paper we will examine what kind of patterns
we can expect and what influence those patterns have on the
implementation of the evolutionary algorithm.
\end{abstract}

>>>>

experiment.aggregates <- data.frame(Experiment=character(),
                                     milliseconds=character(),
                                     IPs=character(),
                                     actualIPs = character(),
                                     PUTss = character(),
                                     actualPUTs = character());

@@

    experiment.aggregates <- rbind( experiment.aggregates,
                                   data.frame( Experiment=i,                   
                                              milliseconds=median(as.integer(this.data$milliseconds)),
                                              IPs=median(as.integer(this.data$IPs)),
                                              actualIPs=median(as.integer(this.data$actualIPs)),
                                              PUTs=median(as.integer(this.data$PUTs)),
                                              actualPUTs=median(as.integer(this.data$actualPUTs)))
                                   )

@@

these.experiments <- c("nooverlap-0","nooverlap","nooverlap-newgraph","nooverlap-newgraph-reboot-cachecrash")
ip.correlations <- data.frame(Experiment=character(),
                              correlation=character())

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-per-minute-cache=32-",i,".csv"))
    this.data.plus1 <- this.data[2:length(this.data$IPs),]
    ip.correlations <- rbind(ip.correlations, 
                             data.frame(Experiment=i,
                                        correlation = cor(this.data[c(1:length(this.data$IPs)-1),]$IPs
                                                         ,this.data.plus1$IPs)))
    time.data <- rbind(time.data,
                       data.frame(Experiment=rep(i,length(this.data$IPs)),
                                  minute=strptime(this.data$time,"%Y-%m-%d %H:%M"),
                                  IPs=as.integer(this.data$IPs))
                       )
}
@

\title{Evolutionary algorithms in a volunteer computing system:
  performance assessment}

@@

\begin{abstract}
In a volunteer distributed computing system, users run a program in
their own machine to contribute to a common effort. If they are
embedded in a web page, collaboration is easy, but also ephemeral. In
this paper we analyze a volunteer evolutionary computing system called
NodIO and try to find out a few rules that encourage volunteer
participation and how to make the most of their contributions to the
evolutionary algorithm. We will show different measures of
participation and contribution to the algorithm and how different
volunteer usage patterns and tweaks in the algorithm contribute to
improvements and leveraging of these contributions. 
\end{abstract}
